---
output: 
  word_document: 
    fig_caption: yes
    fig_width: 11
    toc: yes
---
```{r , echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE}

#ctrname <- "Jordan"
#yearreport <- "2018"

```

---
title: "Annual Review of `r ctrname` Country Operation Plan- `r yearreport`"
author: "MENA office of the Director"
date: "`r Sys.Date()`"
---


```{r include=FALSE, cache=FALSE}

library(ggplot2)
library(ggthemes)
library(rmarkdown)
library(xtable)
library(knitr)
library(pander)  ## library to format regression output in Rmd
library(readxl)

```


```{r , echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE}
#setwd("D:/R-project/focus-analysis") 

##  Loading the 3 dataset - Impact, performance, budget
focus.impact <- read.csv("D:/R-project/focus-analysis/data/impact.csv")
focus.performance <- read.csv("D:/R-project/focus-analysis/data/performance.csv")
focus.budget <- read.csv("D:/R-project/focus-analysis/data/budget.csv")
focus.narrative <- read.csv("D:/R-project/focus-analysis/data/narrative.csv")



framework <- read_excel("D:/R-project/focus-analysis/config/UNHCR-Result-Based-Management.xlsx", sheet = 1) 
#names(framework)
framework<- framework[ !(is.na(framework$Indicator)) ,  ]
framework<- framework[ !(framework$dup2 %in% c('dup')) ,  ]
 # names(framework)

## load all R packages for the analysis
source("D:/R-project/focus-analysis/code/0-package.R")

```


```{r , echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE}

library(reshape2)
## Subset for the country
focus1.impact <-focus.impact[focus.impact$operationName == ctrname, ]
source("D:/R-project/focus-analysis/code/timeindic.R")

focus1.performance <-focus.performance[focus.performance$operationName == ctrname, ]
source("D:/R-project/focus-analysis/code/timeindic2.R")


focus1.budget <-focus.budget[focus.budget$operationName == ctrname, ]
focus1.narrative <-focus.narrative[focus.narrative$operationName == ctrname, ]

```

*** 

# Introduction 






*** 
 
#  Refugee Registration
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/revindic.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Registration"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```


***  
#  Refugee Status Determination (RSD)
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "RSD"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```




***  
#  Resettlement
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Resettlement"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
#  Child Protection
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=16}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "ChildProtection"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
#  Sexual and other forms of gender-based violence (SGBV)
## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=16}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "SGBV"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
#  Education
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Education"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
#  Legal issues
## Indicator selection for this year and potential sourcing
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Legal"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
# Mixed Migration
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Mixed migration"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
#  Statelessness
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/revindic.R")
```
### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Statelessness"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
#  Community Services
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Community Services"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
#  Community Based Protection
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Community Based Protection"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
#  Cash Based Intervention
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Cash"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
#  Communication
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review

### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Communication"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
 
#  Protection Coordination
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "ProtCoordination"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
#  Information Management
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Information Management"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```


***

# Health
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Health"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
# Food Security & Nutrition
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Food"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
# Non Food Item (NFI)
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "NFI"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



*** 
# Shelter
## Indicator selection for this year and potential sourcing
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Shelter"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
 
#  WASH
## Indicator selection for this year and potential sourcing
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "WASH"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```





***
#  Supply
## Indicator selection for this year and potential sourcing
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Supply"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```




***
#  Camp Coordination and Camp Management (CCCM)
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "CCCM"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
 
#  Energy
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/revindic.R")
```


### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/plotindic.R")
```


### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Energy"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
 
#  Environment
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/plotindic.R")
```


### Performance

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Environment"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
 
#  Management
## Indicator selection for this year and potential sourcing
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Management"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
 
#  External Relation
## Indicator selection for this year and potential sourcing
### Impact

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/revindic2.R")
```


## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/plotindic.R")
```

### Performance
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "ExtRel"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***
#  Response Coordination
## Indicator selection for this year and potential sourcing
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/revindic.R")
```

### Performance
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/revindic2.R")
```

## Budget for linked output & objectives
### By Scenario

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=6}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/plotindicBudgetscenario.R")
```

### By Implementer

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/plotindicBudgetimplementerName.R")
```

### By Type

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/plotindicBudget.R")
```


### By Center

```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=10, fig.height=14}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/plotindicBudgetCentername.R")
```


## Indicator review
### Impact
 
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/plotindic.R")
```


### Performance
```{r , echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width = 10, fig.height = 7}
this.subtype <- "Coordination"
source("D:/R-project/focus-analysis/code/plotindic2.R")
```



***




